---
title: "Chapter 3 R Lab"
output: html_notebook
---

The MASS library contains the Boston data set, which records medv (median house value) for 506 neighborhoods around Boston. We will seek to predict medv using 13 predictors such as rm (average number of rooms per house), age (average age of houses), and lstat (percent of households with low socioeconomic status).
To find out more about the data set, we can type ?Boston.
```{r}
library(MASS)
library(ISLR)
names(Boston)
?Boston
```
We will start by using the lm() function to fit a simple linear regression
model, with medv as the response and lstat as the predictor. The basic lm() syntax is lm(y∼x,data), where y is the response, x is the predictor, and
data is the data set in which these two variables are kept.
```{r}
fit1=lm(medv~lstat,data=Boston)
fit1
summary(fit1)
names(fit1)
confint(fit1)
```
The predict() function can be used to produce confidence intervals and prediction intervals for the prediction of medv for a given value of lstat.
```{r}
predict(fit1,data.frame(lstat=c(5,10,15)),interval="confidence")
```
We will now plot medv and lstat along with the least squares regression line using the plot() and abline() functions.
```{r}
plot(medv~lstat,Boston)
abline(fit1)
abline(lm.fit,lwd=3,col="red")
```
Next we examine some diagnostic plots.
```{r}
par(mfrow=c(2,2)) 
plot(lm.fit)
```
Multiple Linear Regression
```{r}
fit2=lm(medv~lstat+age,data=Boston)
summary(fit2)
fit3=lm(medv~.,Boston)
summary(fit3)
library(car) 
vif(lm.fit)
par(mfrow=c(2,2))
plot(fit3)
fit4=update(fit3,~.-age-indus)
summary(fit4)
```
Nonlinear terms and Interactions
```{r}
fit5=lm(medv~lstat*age,Boston)
summary(fit5)
fit6=lm(medv~lstat +I(lstat^2),Boston); summary(fit6)
attach(Boston)
par(mfrow=c(1,1))
plot(medv~lstat)
points(lstat,fitted(fit6),col="red",pch=20)
fit7=lm(medv~poly(lstat,4))
points(lstat,fitted(fit7),col="blue",pch=20)
plot(1:20,1:20,pch=1:20,cex=2)
```
Qualitative predictors
```{r}
fix(Carseats)
names(Carseats)
summary(Carseats)
fit1=lm(Sales~.+Income:Advertising+Age:Price,Carseats)
summary(fit1)
contrasts(Carseats$ShelveLoc)
```




